Systemic risk and contagion effects in Australian financial institutions and sectors

### 2015-05-29 old stuff/obs-(1)-copy.tex
pdj initial

% Title of paper
\title{Systemic risk and contagion effects in Australian financial institutions and sectors}
% List of authors, with corresponding author marked by asterisk
\author{Piet de Jong,  Geoff Loudon and Weihao Choo \\[4pt]
% Author addresses
\textit{Department of Applied Finance and Actuarial Studies\\ Macquarie University, Sydney, NSW 2109.}
\\[2pt]
%E-mail address for correspondence
{piet.dejong@mq.edu.au}}

% Running headers of paper:
\markboth%
% First field is the short list of authors
{De Jong}
% Second field is the short title of the paper
{Systemic risk}

\maketitle

\section{Literature review}

The starting point for the proposed research is the recent literature and the CIFR targeted areas and APRA aims and functions.
This recent literature includes the following
\cite{adrian2011covar},
\cite{acharya2012capital},
\cite{acharya2012measuring}
and \cite{brownlees2010volatility}.   The proposed research aims to extend and apply these techniques particularly in relation to the entities regulated by APRA.   Thus our  broad aim is to develop, implement and bring to bear recent developments in stress testing  on the aims of APRA and the CIFR targeted research areas detailed above.

\section{Improved  measures of contagion and systematic risk}
\renewcommand{\c}{\ensuremath{\mathrm{CoVaR_q}}}
\renewcommand{\v}{\ensuremath{\mathrm{VaR}_q}}

$\covar_q$ as proposed in \cite{adrian2011covar} is a basis for proposed measures contagion, exposure and systemic risk.   It  suffers from a number of drawbacks:
\bi
\i Couched in terms of $\var_q$ containing the scale of the original measurements.   It is worthwhile to have measures and techniques robust to scale.
\i  Conditioning  on $\var_{0.5}$ is undesirable and relatively intractable.  In our proposal we reference stress with respect  to the unconditional $\var_q$.   This permits a more transparent analysis and estimation. 
\i  Our proposed approach  separates out scale effects and interdependence effects and aims to  relates these separately to external variables including shocks and drivers of systemic risk.   Thus $\var_q$ movements due to scale are disentangled from movements due to codependence with separate driver responses.
\ei

\section{Significance of the project and  policy implications}

Understanding the impact of external shocks and their propagation through   the financial system is vital for managing and remediating systemic risk. Effective regulation is dependent upon the development of a robust and reliable set of appropriate risk measures.  We propose new measures of systemic risk that relate marginal and joint distributions separately to external drivers. This allows for more cogent and coherent stress testing as it includes the estimation of contagion effects, exposure effects and systemic risk across related entities and different financial sectors. Improved stress testing, estimation of risk effects and transmission of shocks through the financial system will make for more cogent prudential policy, prudential margin setting and better identify sources of risk to the financial system.

\newcommand{\q}{\mathrm{Q}}
\section{Percentile sensitivity and contagion}\label{perc}

\subsection{Theorem}  Suppose $x$ is a random vector with marginal distributions\footnote{To economise on notation, write $F_j(x)\equiv F_j(x_j)\equiv F(x_j)$ and similar for other vector functions.} 
$$
F(x)\equiv \{F(x_1),\ldots ,F(x_p)\} \equiv (u_1,\ldots,u_p)\equiv u\ .
$$ 
Further suppose $0\le q\le 1$ is given and  $\q(x)$ is the vector of $q$--quantiles
$$
F\{\q(x)\}=q1=\q(u)\ ,
$$
where $1$ is a vector of $p$ ones. 
Define the stress vector with respect to $x_j$ as\footnote{In \cite{adrian2011covar}  $\Delta CoVar_q\equiv q_{y|x=q_x}-q_y$.  Variable $y$  is generally the ``financial system" and hence considered is the change in the \v\ of the system when institution $x$ stressed, with stress  interpreted as $x=q_x$.  On page 10 of their paper they incorrectly state ``... $CoVaR$ conditions on the event that [an] institution is at its VaR level, which occurs with probability $q$."} 
\be{stress}
\frac{\de\q(x)}{\de x_j} \equiv \q(x|u_j>q) - \q(x)\ ,
\ee
where $\q(x|u_j>q)$ is the vector of $q$--quantiles of $x$ given $u_j>q$.    Then if $\q(x)$  is linear in $q$ 
 then
\be{implicit}
\frac{\de\q(x_i)}{\de\q(x_j)} \equiv \frac{\de\q(x_i)/\de x_j}{\de\q(x_j)/\de x_j} =  
\frac{f_j}{f_i} 
 \frac{q_{ij}}{q(1-q)}\cq q_{ij}=C_{ij}(q+q_{ij},q) - q^2\ ,
\ee
where $f_i$ and $f_j$ are the densities of $x_i$ and $x_j$ evaluated at $\q(x_i)$ and $\q(x_j)$ and  $C_{ij}$ is the copula of $(u_i,u_j)$.   
Further if 
$$
s_{ij}\equiv \frac{q_{ij}}{q(1-q)}\ ,
$$ then  $-1\le s_{ij}\le 1$ with $s_{ij}=\pm 1$ if $x_i$ and $x_j$ are comonotonic and counter monotonic, respectively.  If $x_i$ and $x_j$ are independent then  $s_{ij}=0$. If $u_i$ and $u_j$ are exchangeable  then  $s_{ji}=s_{ij}$.

\subsection{Proof}

By definition
$$
\frac{\de\q(u_i)}{\de u_j} \equiv \q(u_i|u_j>q) -q \equiv q_{ij}\ ,
$$
where  $q_{ij}$ is such that
\be{Qdef}
q =  \frac{\P(u_i\le  q+q_{ij},u_j>q)}{1-q}  = \frac{ q+q_{ij}-C_{ij}(q+q_{ij},q)}{1-q}\ ,
\ee
Rearranging yields the second equation in \eref{implicit}.
Now
 \be{first}
 \frac{\de\q(x_i)}{\de x_j}\equiv \q_{q+q_{ij}}(x_i) - \q(x_i) \approx \q'(x_i)q_{ij}= \frac{q_{ij}}{f_i} \ ,
 \ee
where $'$ denotes differentiation with respect to $q$ and the subscript on $\q$ indicates the revised $q$ for the quantile calculation.  The approximation follows from a first order Taylor expansion and is exact if the quantile is linear in $q$.   Similarly
 \be{second}
 \frac{\de\q(x_j)}{\de x_j}\equiv  \q_{q+q(1-q)}(x_j) - \q(x_j)\approx \frac{q(1-q)}{f_j}\ .
 \ee
 Dividing \eref{first} by \eref{second} yields the first equation in  \eref{implicit} and completes the proof.

\subsection{Discussion}  The critical  result is that sensitivities factor into contributions from the ratios of the marginal densities and quantities calculated from the pairwise copulas.  The via  the implicit  equation for $q_{ij}$ in \eref{implicit}, solved using a  root finding algorithm.
  The quantities $q_{ij}$ are implicitly defined from the pairwise copulas. In summary the ``sensitivity" matrix 
$$
S \equiv \frac{\de Q(x)}{\de Q'(x)}\ ,
$$
where $'$ denotes transposition has ones on the diagonal quantities between $\pm 1$ off the diagonal.   The matrix $S$ is called the sensitivity matrix and displays the sensitivity of the $q$--quantile of  each component of $x$ to  stress in the same or other components.

Since $f_i$ and $f_j$ are  the densities evaluated at $\q(x_i)$ and $\q(x_j)$  it follows that the ratio $f_i/f_j$ can be replaced by the ratio of the hazards.   This is  useful in cases were it is practical to model the hazard rather than the density.

\subsection{Implementation}

\fref{fig1} displays the empirical copulas calculated from four weekly closing stock prices labelled anz, cba, mcq and  wbc for $n=761$ weeks from 2000 April 12 through to 2014 October 29.  The empirical copulas are calculated by converting each observation to an empirical percentile and plotting the same against each of the other series percentiles.

\begin{figure}
  \begin{center}
    \includegraphics{fig1.pdf}
    \caption{Pairwise copulas of bank stocks  cba, anz, mqg, wbc, and the overall bank index.  Red lines plot sensitivity $s_{ij}$ as a function of $q$.}\label{fig1}
   \end{center}
\end{figure}

To estimate  $q_{ij}$  at a particular $q$, the second equation in \eref{implicit} is iterated\footnote{The second equation in \eref{implicit} is a contraction mapping and hence has a fixed point.} starting from $q_{ij}=0$ where copulas are estimated as 
$$
\hat C_{ij}(u_i,u_j) \equiv \hat\E\{(p_{ik}\le u_i)(p_{jk}\le u_j)\}\ .
$$
Here $\hat\E$ computes the empirical mean over the cases $k=1,\ldots,n$ and $p_{ik}$ and $p_{jk}$ are the empirical percentiles  of case $k$ of $x_i$ and $x_j$, respectively.

\subsection{Generalisations}
\renewcommand{\r}{\mathrm{R}}
Similar results apply when $\Q(x)$ is replaced by  other risk measures such as $\r(x)\equiv\E\{xr(u)\}$ where $r$ is a given function which acts componentwise and $xr(u)$ denotes componentwise multiplication.  For example if $r(u)=mu^{m-1}$ then  $\r(x)=\E\{\max(x^1,\ldots,x^m)\}$ where  $x^1,\ldots,x^m$ are $m$ independent copies of $x$ and the risk measure is the expected worst outcome in $m$ independent trials.

With $\r(x)$, the analogue of \eref{stress} is 
\be{stress2}
\frac{\de\r(x)}{\de x_j} \equiv \r(x|u_j>r_j) - \r(x_j)\cq r_j\equiv\p\{x_j\le\r(x_j)\} \ .
\ee
This differs from \eref{stress}  in that a different risk measure is used and  $r_j$ replaces $q$.   If  the components of $\r(x)$ are linear in the $r_i$ then
\be{implicit2}
\frac{\de\r(x_i)}{\de\r(x_j)} =  
\frac{f_j}{f_i} 
 \frac{q_{ij}}{q(1-q)}\cq q_{ij}=C_{ij}(r_i+q_{ij},r_j) - r_ir_j\ ,
\ee
where $f_i$ and $f_j$ are the $x_i$ and $x_j$ densities at the $r_i$ and $r_i$ quantiles, respectively.

\section{Systemic risk}
\cite{brownlees2015} describe a model for systemic risk (SRISK) estimated for each financial firm $i$ and each time point $t$.    SRISK of a firm at time $t$ is the expected capital shortfall  it will experience in the period $(t,t+h)$ given a crisis downtown in the market over the same period.    Capital shortfall is defined as the ratio of equity to equity plus debt falling below a certain level $k$.  A crises market is a market return below $c$.

If expected capital shortfall  is zero then SRISK is zero.   The sum of  SRISK's  across all firms is the total SRISK in the economy and each firm contributes either zero or some proportion to the total SRISK in the economy.    Firms with a high  percentage SRISK (denoted SRISK\%) are systemically important and will be  of major concern to regulators.

\subsection{Debt and Equity}

Suppose a firm at time $t$ has debt $D_t$ and equity $W_t$.   Then at $t$, $D_t+W_t$ is the total claim on the firm. 
Regulated firms are generally required to hold a proportion $k$ of total claims $k(D_t+W_t)$ as a prudential margin.    If  $k(D_t+W_t)>W_t$ then, prudentially speaking, the firm has capital shortfall   
$$S_t\equiv k(D_t+W_t)-W_t\ .
$$  
Negative capital shortfall indicates positive working capital.

Concerned with predicting capital shortfall $S_{t+h}$ conditional on a systemic event defined as a market decline below a threshold $c$ over the time horizon $(t,t+h)$.  This is similar to \cite{acharya2012wp}.

\subsection{Returns, leverage and capital shortfall}

Consider a single firm with return $r_t$.   This is the percentage change in value over the period  $(t-1,t)$ known as period $t$.   The arithmetic return over the period $(t,t+h)$ is $\nu_t\equiv r_{t+1}+r_{t+2}+\cdots+r_{t+h}$ and is an $h$ period return.  If $h=1$ then  $\nu_t=r_{t+1}$.

The equity of a firm at time $t+h$ is 
$$
w_{t+h} = (1+\nu_{t})w_t\cq \nu_t\equiv r_{t+1}+\cdots+r_{t+h}\ ,
$$

If the debt of the firm $d_t$  stays constant over the period $(t,t+h)$:   $d_t=d_{t+1}=\cdots=d_{t+h}$  and the capital shortfall i 
\be{cs}
c_{t+h}\equiv  k(d_{t+h}+w_{t+h})-w_{t+h} = k d_{t} - (1-k)(1+\nu_{t})w_t
\ee
 Note  $c_{t+h}$ is a linear in $\nu_t$.

\subsection{Systemic events and systemic risk of a firm}
A systemic event or ``crisis"   occurs in the period $(t,t+h)$ if the market  return $r_{mt}(h)\le c$.   The systemic risk (SRISK)  of  a firm is the expectation of the capital shortfall given  a crisis:
\be{sr}
\mathrm{SRISK}_t\equiv  \E_t\{S_{t+h}|r_{mt}(h)\le c\}  =  [k\ell_t-(1-k)\E_t^c\{r_{t}(h)\}-1]W_t\ .
\ee
where
$$
\mathrm{LRMES}_t \equiv \E^c\{r_{t}(h)\}\equiv \E_t\{r_t(h)|r_{mt}(h)<c\}\ ,
$$
and in terms of this notation:
$$ 
 \mathrm{SRISK}_t = \{k\mathrm{LVG}_t - (1-k)\mathrm{LRMES}_t - 1\}W_t\ .
$$
The condition $D_{t+h}=D_t$ or less strongly $\E_t^c(D_{t+h})=D_t$ indicates the value of debt  does not change if there is a crisis.

Evaluating the systemic risk in a firm requires the evaluation or estimation of the ``crisis" expectation, also called  the long run marginal expected shortfall (LRMES):

$\mathrm{SRISK}_t$ is a point estimate of capital shortfall in a crisis.   Since $S_t$ is linear in $r_t$ the crisis distribution of $S_t$ is known if the conditional distribution of $r_t(h)|r_{mt}(h)<c$ is known.

\subsection{Vector generalisation}

Aggregate systemic risk is 
$$
\mathrm{SRISK}_t = \sum_i \mathrm{SRISK}^+_{it}
$$
where $^+$ indicates the positive part of.   
   The proportion of systemic risk in firm $i$ is then
$$
\mathrm{SRISK\%}_{it} = \frac{\mathrm{SRISK}_{it}^+}{\mathrm{SRISK}_{t}}
$$

\subsection{Example from vlab}
See \fref{vlab} taken on 15 April 2015 from the website http://vlab.stern.nyu.edu

\begin{figure}[htbp]
\caption{default}\label{vlab}
\begin{center}
%\includegraphics[width=15cm]{vlab.pdf}
\end{center}
\end{figure}

\subsection{Discussion points}

\begin{enumerate}
\item  Above is similar to ``stress tests" regularly applied to financial firms.   However above uses only publicly available information
\item  Above approach is forward looking -- ie distribution of future assets conditional on a systemic event.  Markets look at things forwardly so incorporating forward information.
\item  Should have an appropriate $h$ and $c$ -- not too small etc.
\item  Capital shortfall is natural to use since this generates reduced lending activiity etc.
\item Measuring distress a firm is going to suffer conditional on a systemic event affecting the entire system.   Note this is different from capital shortfall conditional on firm default as with credit models.
\item Not concerned with the probability of joint distress of a large proportion of firms in the financial system.   Here systemic risk is determined by the capital shortfall generated distressed institutions conditional on a systemic event.  Framework takes into account joint dependence among firms, as well as their size and degree of leverage.   Do a small number of large financial institutions pose systemic threats to the entire system?  Tail correlations might fail to do so.
\item  Simplifying assumptions are made to deliver a measure that can be easily computed in practice.    Asset structure is captured in a limited sense.   
\item   Measurement approach can be applied to non financial firms.   However these firms are not highly levereged and are not as vulnerable as financial firms.    Not clear how capital shortfall transmits to rest of economy.

\end{enumerate}

\subsection{Static econometric model for systemic risk}

An econometric models  links one period returns $r_{it}$  to the  market return $r_{mt}$ enabling  the calculation of 
LRMES and SRISK.   The approach is to assume $(r_{it},r_{mt})$ are zero mean bivariate normal with volatilities $\sigma_{it}$ and $\sigma_{mt}$ and correlation $\rho_t$.  In this case
$$
\E(r_{it}|r_{mt}<c) = \frac{\rho_t\sigma_{it}}{\sigma_{mt}}\E(r_{mt}|r_{mt}<c)  = \rho_t\sigma_{it}\psi\left(\frac{c}{\sigma_{mt}}\right)\cq \psi(x)\equiv\frac{\phi(x)}{\Psi(x)}\ .
$$
Noting $r_{it}(h)=r_{i,t+1}+\cdots+r_{i,t+h}$ and similarly for $r_{mt}(h)$ then 
$$
\E\{r_{it}(h)|r_{mt}(h)<c\}  = \sqrt{h}\rho_t\sigma_{it}\ \psi\left\{\frac{\ln(1+c)}{\sigma_{mt}\sqrt h}\right\}\ .
$$
{\it Let us emphasize that the [last] formula ... has an error which is due to the fact that we are approximating MES using compound returns rather than arithmetic returns.    In particular [the] formula ... has a negative approximation error  and provides more extreme negative LRMES values.}

\subsection{Modelling systemic risk using a dynamic model}

\cite{brownlees2015} use  data on 95 large US financial firms for the period 2000-2012:   daily equity returns and market capitalization from CRSP; quarterly book values for equity and debt from Compustat.   A   Dynamic Conditional Correlation (DCC) model is estimated for  firm and market returns.  Write
\newcommand{\veps}{\varepsilon}
$$
\cov (r_t|t) = V_tR_tV_t'\cq R_t\equiv \cov(\veps_t|t)\cq \veps_t=V_t^{-1}r_t\ ,
$$
where $R_t$ and  $V_t$  are the correlation and diagonal volatility matrix, respectively, at time $t$.   Volatilities in $V_t$  are estimated using univariate threshold GARCH models.  The estimate of $R_t$ corresponds to the correlations in covariance matrix $C_t$ assuming
$$
(C_t - C) = \alpha (C_{t-1}-C)+\beta (\veps_t\veps'_t-C) \cq C\equiv\cov(\veps_t)\ .
$$
where $C$ is the long run covariance matrix.

\cite{brownlees2015} find the above systemic risk measure  a)  successfully identifies systemically risky firms during the GFC;
b)  predicts capital injections by Fed Reserve; and c) aggregate systemic risk provides early warning of declines in industrial production and higher unemployment.

Thus the model  estimates the beta of a firm equity on a broad market index.
A bivariate volatility model is estimated for the return on the broad market and the equity return of each firm. This model allows volatilities and correlations to evolve.    The estimated process is used to simulate the probability of severely negative outcomes over an extended period. Assuming that firms can only operate if capital is a non--trivial proportion of their total liabilities, SRISK is defined as the capital that would be needed to achieve a market cap that is 8\% of the book value of assets in the event of a crisis. The input to SRISK is size, leverage and risk. Each is important and a firm that wants to reduce its SRISK, can operate on any of these characteristics. A crisis is taken to be a 40\% drop in global equity values over six months. SRISK is computed weekly for firms from about 70 countries and published on the internet at http://vlab.stern.nyu.edu.  In extending this analysis to international markets, the model is naturally generalized to a multivariate volatility model. The data are considered to be the equity return on one firm, the equity return on a global index of equity returns, and perhaps some lags. The use of daily data for assets that are priced in different time zones means that closing prices are not measured at the same time and consequently there may be some important effect from lagged factor returns.

\subsection{Systemic risk based on probabilities}

If $d_t$ and $w_t$ are the debt and equity of a firm at time $t$ then the capital shortfall at time $t$ is 
$$
(1-k) d_t  - k w_t
$$
Basel II assumes $1-k=0.08$ implying there is  positive  capital shortfall if 
$
 0.08 d_t>0.92 w_t
$
or  leverage $d_t/w_t>11.5$ or the log--leverage is greater than $\ln(11.5)=2.44$.

Given the debt and equity, the capital shortfall at time $t$ is zero if 
$$
\frac{k_t}{1-k_t} = \frac{d_t}{w_t}\cq k_t= \frac{d_t/w_t}{1+d_t/w_t} = \frac{d_t}{d_t+w_t}
$$
where $0\le k_t\le 1$  is thought of as a risk index and $k_t/(1-k_t)$ is the leverage or risk odds.

Now consider the situation at time  $t+h$ where $h>0$, 
$$
 k_{t+h}\equiv\frac{d_{t+h}}{d_{t+h}+w_{t+h}} =  \frac{d_t}{d_t+\e^{\nu_{t+h}}w_t}
$$ 
where it is assumed $d_{t+h}=d_t$ and $\nu_{t+h}$ is the $h$ period return over $(t,t+h)$.  The   logit risk/log leverage is
$$
\ell_{t+h}\equiv\ln \frac{k_{t+h}}{1-k_{t+h}} = \ln \frac{d_{t+h}}{w_{t+h}} = \ln d_t - \ln w_t - \nu_{t+h} = \ell_t -\nu_{t+h} \ .
$$
Hence a large positive return $\nu_{t+h}$ implies a lower  risk.  As the logit risk/log leverage  increases to 2.44 the firm approaches the Basel II threshold.

If there are a number of  firms $i$ then $\ell_t$ and $\nu_{t+h}$ are  vectors with components $\ell_{it}$ and $\nu_{it}$, respectively, and in vector terms, $\ell_{t+h}=\ell_t - \nu_{t+h}$.   The aggregate risk is $1'\ell_{t+h}$.

\subsection{Systemic risk}

Systemic risk is defined as the log--leverage in the system as a whole:   that is  aggregate all debt and equity and compute, as above, the log--leverage $\ell_t^+$.    Then
$$
\ell^+_{t+h} = \ln \frac{d^+_t}{w^+_t}-\nu^+_{t+h} =  \ln \sum_i\alpha_{it}\frac{ d_{it}}{ w_{it}} -\nu^+_{t+h}= \ln \Ex_w(\e^{\ell_{it}})-\nu^+_{t+h} \cq \alpha_{it}\equiv\frac{w_{it}}{ w^+_t}\ .
$$
where $\nu_{t+h}^+$ is the aggregate return
$$
\ln \frac{1'w_{t+h}}{1'w_t} = \ln\Ex_w(\nu_{it})
$$
Differentiating with respect to $\ell_{i,t+h}$ yields
$$
\frac{\de \ell^+_{t+h}}{\de \ell_{i,t+h}} = \frac{\alpha_{it}\e^{\ell_{it}}}{\sum_i\alpha_{it}\e^{\ell_{it}}} \frac{\de\nu_{i,t+h}}{\de \ell_{i,t+h}}=\frac{w_{it}\e^{\ell_{it}}}{\sum_iw_{it}\e^{\ell_{it}}}
=\frac{d_{it}}{\sum_id_{it}}=\frac{d_{it}}{d_t^+}\ ,
$$
implying the percentage change in overall forecast leverage respect to a percentage change of the forecast leverage of  firm $i$ is proportional to the proportion of debt in firm $i$.   Further 
$$
\ell^+_{t+h} = \ln \Ex_w(\e^{\ell_{it}})-\nu^+_{t+h} \approx \Ex_d(\ell_{it})-\Ex_d(\nu_{i,t+h})\
$$
Thus the contribution of firm $i$ to the systemic risk is

\subsection{Comparing default probabilities}

Suppose $\ell_{it}$ and $\ell_{t}$ are the risk for firm $i$ and the combination of firms.   Then the excess risk in firm $i$ is
$$
\ell_{it}-\ell_t = \ln \frac{d_{it}}{d_t} - \ln \frac{w_{it}}{w_t} + (\nu_t-\nu_{it})\ .
$$
Thus if firm $i$ has the the same leverage as the average leverage then the excess risk is the underperformance over the time interval $(t,t+h)$.

Note

and hence can define
$$
x
$$

\subsection{Systemic risk}

The total leverage in the system is

a value weighted average of the individual leverages.   The $k_t$ for  capital shortfall for the system as a whole can be
produced from this total leverage.   The logit $\ell_t$ of $k_t$ then yields a risk index for the system as a whole.  Note
$$
\ell_t \equiv \ln \frac{d_{t+h}}{w_{t+h}}=-\nu_t+\ln \sum_i\alpha_{it}\frac{ d_{it}}{ w_{it}}\ne \sum_i \ell_{it}
$$

Can look at
$$
\ell_{it}-\ell_t  = \ln d_{it}-\ln d_t - (\ln w_{it}-\ln w_t) - (\nu_{it}-\nu_t)
$$

Suppose there are a number of firms and define
$$
d_t=\sum_i d_{it}\cq w_t=\sum_i w_{it} \cq  \frac{\ell_{it}}{\ell_t}
$$

The log--odds can be related to other variables.  In many cases the capital injection required is negative indicating capital can be withdrawn from the company without it breaching prudential standards.

\subsection{GARCH-DDC simulation}

We can consider the distribution of the projected log--leverage (pll) conditional on other variables including the market return
$$
\E(\ell_t|\nu_{mt}\le c)  = \ln d_t -\ln w_t -\E(\nu_t|\nu_{mt}\le c)\ .
$$
Alternatively we can consider the  $\alpha$--percentiles of $\ell_t$ denoted $\ell^\alpha_t$ such that
$
\alpha=\P(\ell_t\le \ell_t^\alpha)
$.  Note
$$
\ell_t^\alpha = \ln d_t -\ln w_t -\nu_t^\alpha = \ln \frac{d_t}{w_t}-\nu_t^\alpha\  .
$$

The GARCH-DCC setup delivers forecast or simulated values of $r^s_{t}(h)$, $s=1,\ldots, S$  for each  $t$.      Assume the simulated values are ordered in terms of increasing market returns $r^s_{mt}(h)$ and arranged in an $2\times S$ matrix $C_t$ where  the bottom row is the simulated market return.

This computation is complicated by two things:
\begin{enumerate}
\item  Dividends my be paid  in the period $(t, t+h)$ serving to reduce equity.  Typically at most one dividend  is payable which can be accumulated to  $t+h$ and used to increase equity.   That is for purposes of  assessing model accuracy $w_{t+h}$ is increased by proportion $1+f_{t'}(1+r_{t'})^{t+h-t'}$ where $t\le t'<t+h$ is  ex--dividend date and $f_t$ is the dividend yield.
\item  Debt may change over the period.
\end{enumerate}

In terms of $C_t$ the SRISK measure of \cite{brownlees2015} is the average, along each row of the prefixes.  For example,  the average in row $i$ of the  first $s$ entries is the systemic risk of firm $i$ at time $t$ conditional on  $r_{mt}(h)\le F_{mt}^{-}(s/S)$ where  $F_{mt}$ is the empirical distribution of the  $r^s_{mt}(h)$, $s=1,\ldots,S$.

A default or breach of prudential margins occurs if $c_{it}^s>0$.  The probability of a default if $r_{mt}(h)\le F_{mt}^{-}(v)$ is estimated as 
$$
\hat p_{it}=\frac{\sum_{s=1}^{[vS]}I(c^s_{it}>0)}{[vS]}\ ,
$$
where $v$ is given, for example $v=0.1$.
Joint probabilities of default are estimated similarly: the joint probability of a subset $B$ of firms  breaching their margins is 
estimated as
$$
\hat p_{Bt} = \frac{\sum_{s=1}^{[vS]}\prod_{i\in B} I(c^s_{it}>0)}{[vS]}\ .
$$
These probabilities generally decline with $v$: that is as the market downturn becomes less extreme.

Instead of asking what is the probability of a default (ie breach of prudential regulation) it is meaningful to consider what would $k$ have to be in order for it to be in default at time $t+h$.    Writing this value as
$$
k_t d_t - (1-k_t)\{1+r_t(h)\}w_t = 0 \qquad \implies \qquad k_t=\frac{1}{1+d_t/[\{1+r_t(h)\}w_t]}
$$
This equation can be computed given $r_t(h)$ and hence for every simulated value to arrive at $k_t^s$.    If $d_t\equiv0$ then $k_t=1$ indicating  a healthy state of affairs.  If $d_t/w_t$ is large then $k_t\approx 0$.    Hence as $k_t$ drops there is more danger.

Furthermore
$$
\ln k_t = -\ln \left[1+\{1+r_t(h)\}^{-1}\frac{d_t}{w_t}\right]\approx -\{1+r_t(h)\}^{-1}\frac{d_t}{w_t}\approx -\e^{-r_t(h)}\frac{d_t}{w_t}
$$
$$
\kappa_t \equiv \ln(-\ln k_t) \approx  \ln (d_t) - \ln (w_t) - r_t(h)
$$
A large value for $\kappa_t$ indicates

To study the time series and cross sectional behaviour of $\hat p_{it}$, it is useful to define the  normal scores 
$$
z_{it} \equiv \Phi^-(\hat p_{it})\cq i=1,\ldots, n\cq t=1,\ldots, T\ .
$$
Defining  $z_t\equiv (z_{1t},\ldots,z_{nt})'$ then a firm is systemically important if it is highly collinear with the other scores.

An entropy based measure of systemic risk is
$$
H_t = -\E(\ln p_{Bt})\equiv -\sum_B p_{Bt}\ln p_{Bt}\ .
$$

Systemically important firms are those which, when in default, are highly likely to be associated with a joint default.
joint probability of matrix is then 
$$
  P_t\equiv \frac{1}{S} I_tI_t'\cq  I_t = I(\rho^s_{it}>0)
$$

 can define the probability of a firm going in default as
$$
\hat p_{it}\equiv \frac{\sum_{s=1}^SI(\rho_{it}^s>0)}{S}
$$ 
In terms of this notation the probability of all firms going bankrupt and non

\subsection{Time--varying copula model}

Suppose $\delta\ge 1$ and the rotated Gumbel copula modelling lower tail dependence:
$$
C_\delta(u,v) = u+v-1+\e^{-[\{-\ln(1-u)\}^{\delta}+\{-\ln(1-v)\}^{\delta}]^{1/\delta}}
$$
Further suppose a sequence
$$
\delta_{t+1} = 1+\left(\omega + \alpha \frac{\sum_{s=0}^{m-1}|u_{t-s}-v_{t-s}|}{m}+ \beta\delta_t\right)^2\ .
$$
Note $\delta_t$ is always greater than 1.  \cite{patton2006modelling} has more details.   The model is fitted by estimating marginal models first and then by maximizing the copula likelihood using the fitted uniform marginals.

\subsection{Data  used in \cite{brownlees2015} }

\begin{itemize}
\item Large US financial firms (ie capitalization greater than 5bln US)
\item Jan 3, 2000 through to Dec 31, 2012:  not all companies continuously traded
\item Daily returns and market capitalization from CRSP
\item Quaterly book value of equity and debt from COMPUSTAT.
\item SIC codes used to segment firms into 4 industry groups (Depositries (29), Broker Dealers (10), Insurance (34) and Others (22))
\end{itemize}

SRISK is computed with the parameters $k=0.08$, $c=-0.1$, $h=22$ (a month).  SRISK computed at end of each month using all available data at that data, therefore no look ahead bias.

LRMES computed with the GARCH-DCC model for each firm.   Uses all available data starting from Jan 3, 2000 to end of each month.

\subsection{Older stuff}

$$
\E^c(r_{it}) \equiv \E(r_{it}|u_{mt}\le c^*)\cq c^*=\E\{(r_{mt}\le c)\}\ ,
$$
where $u_{mt}$ is the percentile of $r_{mt}$.
Given a joint distribution for $(r_{it},r_{mt})$ the distribution is simulated and
\be{sim}
\E^c(r_{it}) \approx \frac{\hat \E\{(r_{mt}\leq c)r_{it}\}}{\hat \E\{(r_{mt}\leq c)\}}= \frac{\hat\E\{(u_{mt}\leq c^*)F^-_{it}(u_{it})\}}{c^*}\ ,
\ee
where the $r$ values in the middle expressions denote simulated values and $\hat\E$, averages over the simulated values.   The $u_{it}$ and $u_{mt}$ are the percentiles of $r_{it}$ and $r_{mt}$, respectively.

The right hand expression in \eref{sim}  suggests using a copula to model the joint distributions $(r_{it},r_{mt})$.  Simulate $(u_{it},u_{mt})$, from the copula, discarding pairs with $u_{mt}>c^*$.   For each accepted $(u_{it},u_{mt})$  determine the actual return using the respective marginal distributions.   Issues to be addressed are:
\bi
\i Are the marginal distributions time invariant?  Could have situation where the marginal distribution evolves over time and/or is state dependent
\i Is the copula time invariant?   Could have situation where the copula is state dependent.    
\ei

The first step here is to examine the marginal distributions of the returns and the empirical copula of returns.

{\bf Comment.}  With the DCC model both volatilities and correlations have a time dependent structure.  These are modelled separately.
An alternative approach is where ...

{\bf \cite{engle2014dynamic}} describes a new approach to estimating time varying regression coefficients.   The approach is called Dynamic Conditional Beta (DCB).   Consider $(y_t,x_t)$ where  $y_t$  and $x_t$ are vectors.  Interested in $\E_t(y_t|x_t)$.   This is expression  may be linear in $x_t$ and depending on the past information set.  Write
\newcommand{\F}{{\cal F}}
$$
(y_t,x_t)|\F_{t-1} \sim N(\mu_t,H_t) \implies y_t|x_t,\F_{t-1}\sim N\{\mu_{yt}+B_t(x_t-\mu_{xt}), C_{yy,t}\}
$$
where
$$
B_t= H_{yx,t}H^-_{xx,t}\cq  C_{yy,t}= H_{yy,t}-B_tH_{xx,t}B'_t\ .
$$
These expressions depend on the time varying covariance matrix $H_t$.    For implementation we need a model for $\mu_t$ and $H_t$.

\section{TARCH modelling}

>>>>

\section{Weihao's approach}

Univariate stressing leads to the stressed put expectation
$$
\E\{\phi(r_m)p_{it}\} = \int  f(r_m)\phi(r_m)\E(p_{it}|r_m) \de r_m = \int f_\phi(r_m) \E(p_{it}|r_m) \de r_m
$$
where $f$ is the original density of a market factor $r_m$ and $f_\phi=f\times \phi$ is the assumed density. Note $\phi$ may act on $r_m$ or its percentile rank $u_m$. The intent of $\phi$ is the enlarge the likelihood of ``bad" outcomes of $r_m$.

Bivariate stressing yields
$$
\E\{\phi(r_m,r_n)p_{it}\} = \int \int f(r_m,r_n)\phi(r_m,r_n) \E(p_{it}|r_m, r_n) \de r_m \de r_n
$$
$$
= \int \int f_\phi(r_m,r_n) \E(p_{it}|r_m, r_n) \de r_m \de r_n
$$
where $r_n$ is another market factor and $f$ is now the joint density of $(r_m,r_n)$. The assumed joint density is $f_\phi=f\times \phi$, which again enlarges the joint likelihood of ``bad" outcomes of $(r_m,r_n)$. For example $f_\phi$ may have stronger tail dependence than $f$, which can be achieved by either selecting a copula which has stronger tail dependence, or setting up $\phi$ as $\phi(u_mu_n)$ where $\phi$ is decreasing. Marginal distributions of $r_m$ and $r_n$ may be altered or unchanged. If unchanged then
$$
f(r_n) = \int f(r_m,r_n) \de r_m = \int f_\phi(r_m,r_n) \de r_m
$$
or
$$
1 = \int f(r_m)c(u_m,u_n) \de r_m = \int f(r_m)\phi(r_m,r_n) c(u_m,u_n) \de r_m
$$
since $f(r_m,r_n)=f(r_m)f(r_n)c(u_m,u_n)$.
